\documentclass{article}
\usepackage{fancyhdr}
\usepackage{geometry}
\usepackage{hyperref}

\geometry{letterpaper, left=2cm, right=2cm, top=2cm, bottom=2cm}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[LE,RO]{\thepage}
\fancyfoot[RE,LO]{\copyright\hspace{0.25em}codeabode 2025. \href{https://codeabode.co}{\underline{codeabode.co}}}

\title{\vspace{-3em}Assignment: Print \& Basic Vars\vspace{-3em}}

\begin{document}
\fontsize{14}{16}\selectfont
\maketitle
\vspace{-1em}

\begin{itemize}
    \item Basic Python Types
    \item Format-Strings
    \item String concatenation
\end{itemize}

Before we move to conditionals, it is \textbf{imperative} that this foundation is solidified.

\section{Monday}

Create a profile for the following person. \\
Print in the format \verb|"name=...,age=...,hobby=..."| using commas in print. \\ 

\begin{itemize}
    \item Name: Aditya
    \item Location: San Francisco
    \item Favorite Color: Blue
    \item Age: 22
    \item Hobby: Cooking
\end{itemize}

Now, print the same profile in a sentence format. Use \textbf{f-string} to format the sentence.

\section{Tuesday}

Create a profile for the following person. Print \verb|"name=...,age=...,hobby=..."| using \textbf{string concatenation (+)}.

\begin{itemize}
    \item Name: John
    \item Location: California
    \item Favorite Color: Red
    \item Age: 30
    \item Hobby: Surfing
\end{itemize}

Now, print the same profile in a sentence format. Use \textbf{f-string} to format the sentence.

\section{Wednesday}

Create a profile for a person and print it in the format \verb|"name=...,age=...,hobby=..."| using \textbf{commas}.

\begin{itemize}
    \item Name: Jane
    \item Location: Texas
    \item Favorite Color: Green
    \item Age: 25
    \item Hobby: Gaming
\end{itemize}

Now, print the same profile in a sentence format. Use \textbf{f-string} to format the sentence.


\section{Thursday}

Create a profile for the following person. Print \verb|"name=...,age=...,hobby=..."| using \textbf{string concatenation (+)}.

\begin{itemize}
    \item Name: Mary
    \item Location: London
    \item Favorite Color: Yellow
    \item Age: 35
    \item Hobby: Reading
\end{itemize}

Now, print the same profile in a sentence format. Use \textbf{f-string} to format the sentence.

\section{Friday}

Challenge day! Today, I want you to mix it up. \\

Instead of writing \verb|name="..."|, write \verb|...="name"|. For example, you're going to write \verb|aditya="name"|. See how this modification changes your sentences in the output.  \\

Make a profile for yourself including the following:

\begin{itemize}
    \item Name
    \item Location
    \item Color
    \item Age
    \item Hobby
\end{itemize}

Print each variable to the console in a sentence-like format, making use of f-string to format the sentence.

\end{document}
